Software Quality Assurance in INDIGO-DataCloud project: a converging evolution of software engineering practices to support European Research e-Infrastructures

### 2019-12-05 paper-jgc.tex
Add clarification for Grid jobs

Project monitoring and reporting mechanisms allowed to assess the risks, efforts and documentation
produced. Development guidelines \cite{datagridguide} were produced, covering the various phases, including
1) packaging, 2) test and validation, and 3) style and naming convention. A set of quality indicators
\cite{datagridindicators} were defined to measure the efficiency of the system from the user perspective. 
Due to the developmental nature of DataGrid project, they solely consider the \textit{crude efficiency} 
metric as the relevant indicator to track the quality and performance of the core software, also known as
\emph{middleware}
in Grid terminology. This metric considered the success rate of all the jobs submitted by users using the 
production testbed, so that all the failures of the middleware were included in the statistic \cite{avellino2004datagrid}. However, it
also accounted for the failures in the remaining pieces in the job submission chain, such as the user application 
software or the targeted datacenter deployment. Even so, as it can be observed in Fig.~\ref{fig:efficiency}, 
the crude efficiency showed a positive trend over the months that followed, with the unique exception of the 
LCG--1 middleware distribution.
\begin{figure}[h]
\centering
%\includegraphics[width=0.8\textwidth, height=50mm]{images/datagridEff.png}
\includegraphics[width=1\textwidth]{images/datagridEff.png}
\caption{Efficiency \% = Number of jobs successfully completed / Total Number of jobs submitted: results are 
provided for the different DataGrid's EDG middleware distributions released throughout the project. Note that the figure
includes metrics of the same release (EDGv1.4) for three Large Hadron Collider (LHC) experiments.}
\label{fig:efficiency}
\end{figure}

>>>>

Project monitoring and reporting mechanisms allowed to assess the risks, efforts and documentation
produced. Development guidelines \cite{datagridguide} were produced, covering the various phases, including
1) packaging, 2) test and validation, and 3) style and naming convention. A set of quality indicators
\cite{datagridindicators} were defined to measure the efficiency of the system from the user perspective. 
Due to the developmental nature of DataGrid project, they solely consider the \textit{crude efficiency} 
metric as the relevant indicator to track the quality and performance of the core software, also known as
\emph{middleware}
in Grid terminology. This metric considered the success rate of all the Grid jobs submitted by users using the 
production testbed, so that all the failures of the middleware were included in the statistic \cite{avellino2004datagrid}. However, it
also accounted for the failures in the remaining pieces in the job submission chain, such as the user application 
software or the targeted datacenter deployment. Even so, as it can be observed in Fig.~\ref{fig:efficiency}, 
the crude efficiency showed a positive trend over the months that followed, with the unique exception of the 
LCG--1 middleware distribution.
\begin{figure}[h]
\centering
%\includegraphics[width=0.8\textwidth, height=50mm]{images/datagridEff.png}
\includegraphics[width=1\textwidth]{images/datagridEff.png}
\caption{Efficiency \% = Number of jobs successfully completed / Total Number of jobs submitted: results are 
provided for the different DataGrid's EDG middleware distributions released throughout the project. Note that the figure
includes metrics of the same release (EDGv1.4) for three Large Hadron Collider (LHC) experiments.}
\label{fig:efficiency}
\end{figure}
